Adapting bootstrap to our problem - Part 2

### 2024-07-11 adapt_boot2.Rmd
Not done yet v2

  df_sample$step <- rep(0, nrow(df_sample))
  for (line in unique(df_sample$l)) {
    df_sample$step <- as.numeric(df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + as.numeric(df_sample$step != 0)*df_sample$step
  }

>>>>

  df_sample$step <- rep(0, nrow(df_sample))
  for (line in unique(df_sample$l)) {
    print(line)
    df_sample$step <- as.numeric(df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + as.numeric(df_sample$step != 0)*df_sample$step
  }
